<!-- badges go here -->
[![Say Thanks!](https://img.shields.io/badge/Say%20Thanks-!-1EAEDB.svg)](https://saythanks.io/to/JohnCoene)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)

library(htmltools)
```

```{r, echo=FALSE}
br()
br()

div(
  class = "row",
  div(
    class = "col-md-4",
    img(
      src = "logo.png",
      class = "img-responsive responsive-img"
    )
  ),
  div(
    class = "col-md-8",
    p(
      "Retrieve the World Economic Forum's Agenda articles."
    ),
    p(
      tags$a(
        tags$i(class = "fa fa-code"),
        class = "btn btn-primary",
        href = "reference/index.html",
        style = "margin-bottom: 5px;",
        "Reference"
      ),
      tags$a(
        tags$i(class = "fa fa-github"),
        class = "btn btn-default",
        href = "https://github.com/news-r/weforum",
        style = "margin-bottom: 5px;",
        "Repository"
      )
    )
  )
)
```

## Installation

You can install the package with `remotes` from Github, see [changes](news/index.html).

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("news-r/weforum") # github
```

## Example


```{r}
library(weforum)

# list endpoints
(endpoints <- wef_endpoints())
```

The above returns basic endpoints, responses from the calls above will include other endpoints, `weforum` lets you dynamically call those. Let's demonstrate with an example.

```{r}
# get some articles
articles <- wef_articles_list() 

nrow(articles[[1]])
```

This returns a nested list, of 25 articles by default. As explained above it includes more endpoints.

```{r}
attr <- articles[[1]]$attributes
names(attr)[grepl("endpoint", names(attr))]
```

You can call those endpoints with `wef_call`.

```{r}
data <- purrr::map(attr$api_endpoint, wef_call)

length(data)
```
