---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)

![weforum logo](https://www.weforum.org/assets/logo-b66768797e3f785791fd157ffc33c27eeca6d5100b7f34d418f50d206f1a8004.svg)

Interface to the [World Economic Forum's](https://www.weforum.org/) website [API](https://api.weforum.org/), containing over 40,000 articles.

## Install

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("news-r/weforum")
```

## Functions

- `wef_articles_list`
- `wef_articles_channels`
- `wef_articles_content_types`
- `wef_articles_origins`
- `wef_collections`
- `wef_communities`
- `wef_events`
- `wef_event_sessions`
- `wef_projects`
- `wef_reports`
- `wef_sf_accounts`
- `wef_topics`
- `wef_streams`
- `wef_updates`
- `wef_endpoints`

## Examples

```{r}
library(weforum)

# list endpoints
endpoints <- wef_endpoints()
```

The above returns basic endpoints, responses from the calls above will include other endpoints, `weforum` lets you dynamically call those. Let's demonstrate with an example.

```{r}
# get some articles
articles <- wef_articles_list() 

nrow(articles[[1]])
```

This returns a nested list, of 25 articles by default. As explained above it includes more endpoints.

```{r}
attr <- articles[[1]]$attributes
names(attr)[grepl("endpoint", names(attr))]
```

You can call those endpoints with `wef_call`.

```{r}
data <- purrr::map(attr$api_endpoint, wef_call)

length(data)
```
